Apropos Replacement \newline (Extended Abstract)

### 2011-12-25 paper.tex
Fix a duplication

In this paper we discuss the limitations of the traditional implementation of
\textit{\textit{\textit{apropos(1)}(1)}}, how did we solve those limitations in our implementation
and what other modern implementations are available out there
our own implementation.
\section{Introduction}
The classical version of \textit{apropos(1)} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords would hardly take few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.

>>>>

In this paper we discuss the limitations of the traditional implementation of
\textit{apropos(1)}, how did we solve those limitations in our implementation
and what other modern implementations are available out there
our own implementation.
\section{Introduction}
The classical version of \textit{apropos(1)} has been implemented by simply
indexing the keywords in the NAME section of the man pages in a plain text file
(whatis.db) [2]
and performing searches on it. The reason for this simple design was most
probably lack of computing resources in the early days. The plain text file
consisting of keywords would hardly take few hundreds of kilo bytes of disk space
and performing search on a plain text file is also not very hard.
